hbm_paper_results

### 2024-05-20 paper_main_results.Rmd
updated, cleaned, and rerun

* `./cubic_scripts/R_scripts/stats_tests.R`
1. `ukb_curation-eda.Rmd`
2. `qsub_combat.sh` -> `/cubic_scripts/R_scripts/combat_apply.R`
3. `qsub_basic_gamlss.sh` -> `/cubic_scripts/R_scripts/fit_basic_mod.R`
4. `qsub_centiles.sh` -> `/cubic_scripts/R_scripts/fit_centiles.R`
5. `gamlss_parse.sh` -> `/cubic_scripts/R_scripts/gamlss_parser.R`

@@

#also load raw data
ukb_cn_df <- fread("/Users/megardn/Desktop/BGD_Repos/combat_biovar/data/ukb_to_model/ukb_CN_data_simsites.csv")

#years for plotting
ukb_cn_df <- ukb_cn_df %>%
  mutate(age_years = age_days/365.25)

@@

pulled variance from cubic using `scp -r 'gardnerm@cubic-login.uphs.upenn.edu:/cbica/home/gardnerm/combat-biovar/ukb_basic/centile_csvs/*_variance.csv' .`

Get predicted centiles
- pulled from cubic using `scp -r 'gardnerm@cubic-login.uphs.upenn.edu:/cbica/home/gardnerm/combat-biovar/ukb_basic/centile_csvs/*_predictions.csv' .`

@@

  # Add a "Source_File" column with the file name
  data <- data %>%
    mutate(Source_File = as.factor(basename(file))) %>%
    mutate(dataset = sub("_data_predictions.csv", "", Source_File))

@@

#drop refA sites, not using for these analyses
combined_preds <- combined_preds %>%
  dplyr::filter(!grepl('_refA', dataset)) #drop refA levels
```

@@

Get errors
- pulled centile/z error calcs from cubic using `scp -r 'gardnerm@cubic-login.uphs.upenn.edu:/cbica/home/gardnerm/combat-biovar/ukb_basic/centile_csvs/*_diffs.csv' .`

@@

#drop refA sites, not using for these analyses
diffs.df <- diffs.df %>%
  dplyr::filter(!grepl('_refA', dataset)) #drop refA levels
```

Get subject-wise summaries
- pulled from cubic using `scp -r 'gardnerm@cubic-login.uphs.upenn.edu:/cbica/home/gardnerm/combat-biovar/ukb_basic/centile_csvs/subject-wise/*.csv' .`

@@

#drop refA sites, not using for these analyses
subj_sum.df <- subj_sum.df %>%
  dplyr::filter(!grepl('_refA', dataset)) #drop refA levels
```

@@

```{r, eval=FALSE}
full_cent_res <- centile.t.tests.full_result(diffs.df, feature_list=pheno_abs.diff.list)
saveRDS(full_cent_res, "./derivatives/ukb_basic/featurewise_cent_t_tests_all_out.RDS") #running once and saving because it takes a long time
```

@@

Little plot
```{r}
#get means w/in feature 
mean.diffs.long <- diffs.df %>%
  dplyr::select(sex, dataset, pheno_abs.diff.list) %>%
  dplyr::filter(!grepl('_refA', dataset)) %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE)) %>%
  group_by(dataset) %>%
  summarize(across(starts_with("abs.diff_"), mean)) %>%
  ungroup() %>%
  pivot_longer(cols=starts_with("abs.diff_"), values_to="centile_abs.diff", names_to = "pheno", names_prefix = "abs.diff_") %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)),
      label = sub("_[^_]*_", "_", pheno))
```

```{r, eval=FALSE}
dataset_names <- c(ukb_CN = "Raw Data", cf = "ComBat w/o Covar", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")
dataset_colors <- c(cf = "#3D5983FF", cf.lm = "#5A8A54FF", cf.gam ="#262626FF", cf.gamlss ="#CFB023FF")

cent.diffs.plot <- mean.diffs.long %>%
  dplyr::filter(dataset != "ukb_CN") %>%
  mutate(centile_abs.diff = centile_abs.diff*100) %>% #for visuals
  ggplot() +
  geom_histogram(aes(x=centile_abs.diff, fill=dataset, y = stat(width*density)), color="black", alpha=0.6, position="identity") +
  theme_linedraw(base_size = 11) +
  facet_wrap(~pheno_cat) +
  scale_y_continuous(labels = scales::percent) + 
  scale_fill_manual(values=dataset_colors, name = "ComBat \nConfiguration", labels=dataset_names) +
  labs(y="Percent Features", x = "Mean Absolute Centile Error") +
  ggtitle("Absolute errors in centile scores of brain structure features across ComBat processing pipelines")
cent.diffs.plot

@@

```{r}
dataset_names <- c(ukb_CN = "Raw Data", cf = "ComBat w/o Covar", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")

@@

global_cent_errs_plot <- global_abs.diffs %>%
  dplyr::filter(dataset == "cf.lm" | dataset == "cf.gam" | dataset == "cf.gamlss") %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         pheno = factor(pheno, levels = c("WMV", "GMV", "sGMV", "Ventricles"), ordered = TRUE),
         abs.diff = abs.diff*100) %>% #for visuals
  ggplot(aes(pheno, abs.diff)) +
  geom_violin(aes(x=pheno, y=abs.diff, fill=dataset, color=dataset), scale="count") +
  theme_linedraw(base_size = 11) +
  scale_fill_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  #WMV
geom_signif(y_position = c(29, 30.5, 4), xmin = c(0.7, 0.7, 1), 
              xmax = c(1, 1.3, 1.3), annotation = c("***","***", "***"),
              tip_length = 0, vjust = 0.6) +
  #GMV
  geom_signif(y_position = c(30, 31.5, 3), xmin = c(1.7, 1.7, 2), 
              xmax = c(2, 2.3, 2.3), annotation = c("***","***", "***"),
              tip_length = 0, vjust = 0.6) +
  #sGMV
  geom_signif(y_position = c(28, 29.5, 2.8), xmin = c(2.7, 2.7, 3), 
              xmax = c(3, 3.3, 3.3), annotation = c("***","***", "***"),
              tip_length = 0, vjust = 0.6) +
  #Ventricles
  geom_signif(y_position = c(24, 25.5, 7.5), xmin = c(3.7, 3.7, 4), 
              xmax = c(4, 4.3, 4.3), annotation = c("***","***", "***"),
              tip_length = 0, vjust = 0.6) +
  labs(y="Absolulte Centile Error", x = "Feature") +
  theme(plot.title = element_text(size=12))
global_cent_errs_plot
# ggsave("figs/global_centile_errors.jpeg", global_cent_errs_plot)
```

All features:
```{r}
long_abs.diffs <- diffs.df %>%
  dplyr::filter(dataset == "cf.lm" | dataset == "cf.gam" | dataset == "cf.gamlss") %>% #drop refA levels
  dplyr::select(participant, sex, age_days, sim.site, dataset, paste0("abs.diff_", pheno_list)) %>%
  pivot_longer(cols=starts_with("abs.diff_"), names_to="pheno", names_prefix="abs.diff_", values_to = "abs.diff") %>%
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         abs.diff = abs.diff*100,
         pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)))

long_abs_diff.plt <- long_abs.diffs %>%
  ggplot(aes(pheno, abs.diff)) +
  geom_violin(aes(x=pheno, y=abs.diff, fill=dataset, color=dataset), scale="count") +
  theme_linedraw(base_size = 11) +
  scale_fill_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  labs(y="Absolulte Centile Error", x = "Feature") +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust=0.4, size=6), legend.position="top") +
  facet_wrap(~pheno_cat, nrow=4, scales="free")
ggsave("figs/all_abs_err_plt_wlabels.jpeg", long_abs_diff.plt, width=13, height=10.5, units="in")

long_abs.diffs %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  ggplot(aes(pheno, abs.diff)) +
  geom_violin(aes(x=interaction(pheno,pheno_cat, sep = "&"), y=abs.diff,  fill=dataset, color=dataset), scale="count") +
  theme_linedraw(base_size = 11) +
  scale_fill_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  labs(y="Absolulte Centile Error", x = "Feature") +
  guides(x = ggh4x::guide_axis_nested(delim = "&")) +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust=0.4, size=6), ggh4x.axis.nesttext.x = element_text(angle = 90, vjust=0.4), legend.position="top")

# ggsave("figs/global_centile_errors.jpeg", global_cent_errs_plot)
```

plot median on brain
```{r}
#get median w/in feature 
med.diffs.long <- diffs.df %>%
  dplyr::select(sex, dataset, pheno_abs.diff.list) %>%
  dplyr::filter(dataset %in% c("cf.lm", "cf.gam", "cf.gamlss")) %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE)) %>%
  group_by(dataset) %>%
  summarize(across(starts_with("abs.diff_"), median)) %>%
  ungroup() %>%
  pivot_longer(cols=starts_with("abs.diff_"), values_to="median_centile_abs.diff", names_to = "pheno", names_prefix = "abs.diff_") %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)),
      label = sub("_[^_]*_", "_", pheno))

@@

dataset_names <- c(ukb_CN = "Raw Data", cf = "ComBat w/o Covar", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")
#var plot
med.diffs.plot.df <- med.diffs.long2 %>%
  dplyr::filter(pheno_cat != "Global Volume") %>%
  dplyr::filter(!grepl('_refA', dataset)) %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         median_centile_abs.diff = median_centile_abs.diff*100)

med.diffs.plot <- ggplot(med.diffs.plot.df) +
  theme_linedraw(base_size=12) +
  ggseg::geom_brain(atlas = dk_nomed, 
             position = position_brain(hemi ~ side),
             aes(fill = median_centile_abs.diff)) +
  facet_grid(dataset ~ pheno_cat, labeller = labeller(dataset = as_labeller(dataset_names))) + 
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=2/3, plot.margin = margin(1,1,1,1, 'pt')) +
  paletteer::scale_fill_paletteer_c("grDevices::Oslo", name = "Median Absolute Centile Error", limits = c(0, 7.5)) #
# med.diffs.plot
```

```{r}
#plot global
med.diffs.plot.global.df <- med.diffs.long2 %>%
  dplyr::filter(pheno_cat == "Global Volume") %>%
  dplyr::filter(!grepl('_refA', dataset)) %>% #drop refA levels
  dplyr::select(!c(label, region, hemi)) %>% #drop cols corresponding to dk regions
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         median_centile_abs.diff = median_centile_abs.diff*100)

med.diffs.plot.global <- ggplot(med.diffs.plot.global.df) +
  ggseg::geom_brain(atlas = aseg_cerebrum, 
             aes(fill = median_centile_abs.diff),
             side = c("coronal")) +
  #scale_fill_gradient2() +
  facet_grid(dataset~pheno_cat) + 
  theme_linedraw(base_size=12) +
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=, plot.margin = margin(1,1,1,1, 'pt'), strip.text.y = element_blank()) +
  paletteer::scale_fill_paletteer_c("grDevices::Oslo", name = "Median Absolute Centile Error", limits = c(0, 7.5))
# med.diffs.plot.global
```

Combine plots - need to keep playing around to make the spacing pretty when it saves out
```{r}
p_diff <- ggarrange(
  med.diffs.plot.global, med.diffs.plot,
  ncol=2, nrow=1, 
  widths = c(.95, 3.1),
  #labels=c("A", "B"),
  #hjust=0.01,
  align = "hv",
  common.legend = TRUE, legend = "bottom"
  )

# p_diff_annotate <- annotate_figure(p_diff)
# p_diff_annotate
```

Quick comp of cf.gam and cf.gamlss

```{r}
ns_gam_gamlss_comp <- full_cent_res %>%
  dplyr::filter(comp=="cf.gamlss_cf.gam" & sig_fdr == TRUE & bigger_group == "cf.gamlss")
nrow(ns_gam_gamlss_comp)
```

**21 regions where ComBat GAM is better than ComBat-LS! All cortical thickness -> 206-21 = 185 regions where ComBat-LS fits better.

@@

check for skew (welch t.test vs ranked welch t test)
```{r, eval=FALSE}
for (pheno in pheno_list){
  val <- paste0("diff_", pheno)
  p <- ggplot(diffs.df, aes(x = diffs.df[[val]], fill= sex, color=sex)) +
      geom_histogram(alpha=0.5, position="identity") +
    ggtitle(val) +
    facet_wrap(~dataset, scales="free")
print(p)
}
```

```{r, eval=FALSE}
for (cf in c("cf.gam", "cf.gamlss")) {
  for (pheno in vol_list_global){
  val <- paste0("diff_", pheno)
  med.df <- diffs.df %>%
    dplyr::filter(dataset == cf) %>%
    group_by(sex) %>%
    summarize_at(val, median, na.rm=FALSE)

@@

```{r, message=FALSE, eval=FALSE}
sex_t_tests_in_feat.df <- sex.bias.feat.t.tests(diffs.df, feature_list=pheno_diff_list)
saveRDS(sex_t_tests_in_feat.df, "./derivatives/ukb_basic/featurewise_cent_sexbias_all_out.RDS")
```

@@

```{r,eval=FALSE}
#view combat gam and combat LS ns
ns.sex_diff_filt.gam <- sex_t_tests_in_feat.df %>%
  dplyr::filter(sig_fdr==FALSE & dataset =="cf.gam") %>%
  arrange(pheno)
ns.sex_diff_filt.gamlss <- sex_t_tests_in_feat.df %>%
  dplyr::filter(sig_fdr==FALSE & dataset =="cf.gamlss") %>%
  arrange(pheno)
```

@@

```{r}
dataset_names <- c(ukb_CN = "Raw Data", cf = "ComBat w/o Covar", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")
#var plot
sex.var.plot.df <- sex_t_tests_to_plot %>%
  dplyr::filter(pheno_cat != "Global Volume") %>%
  dplyr::filter(dataset %in% c("cf.lm", "cf.gam", "cf.gamlss")) %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         median_sex_diff = case_when(sig_fdr == FALSE ~ NA,
                                     TRUE ~ median_sex_diff*100))

sex.var.plot <- ggplot(sex.var.plot.df) +
  theme_linedraw(base_size=12) +
  ggseg::geom_brain(atlas = dk_nomed, 
             position = position_brain(hemi ~ side),
             aes(fill = median_sex_diff)) +
  #scale_fill_gradient2() +
  # ggseg::geom_brain(data=med_wall, atlas = dk, 
  #            position = position_brain(hemi ~ side),
  #            aes(fill=median_sex_diff)) +
  facet_grid(dataset ~ pheno_cat, labeller = labeller(dataset = as_labeller(dataset_names))) + 
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=2/3, plot.margin = margin(1,1,1,1, 'pt')) +
  paletteer::scale_fill_paletteer_c("grDevices::Cork", name = "Male - Female Median \nCentile Error", limits = c(-6, 6)) #
saveRDS(sex.var.plot, file="figs/sex_var_plot.RDS")
```

>>>>

* `./cubic_scripts/R_scripts/stats_tests.R`
1. `ukb_curation-eda.Rmd`
2. `qsub_combat.sh` -> `/cubic_scripts/R_scripts/combat_apply.R`
3. `qsub_basic_gamlss.sh` -> `/cubic_scripts/R_scripts/fit_basic_mod.R`
4. `qsub_centiles.sh` -> `/cubic_scripts/R_scripts/fit_centiles.R`
5. `gamlss_parse.sh` -> `/cubic_scripts/R_scripts/gamlss_parser.R`
6. `qsub_summarize_subj_centiles.sh` -> `/cubic_scripts/R_scripts/summarise_cent_subj-wise.R`

@@

#also load raw data
raw_df <- fread("/Users/megardn/Desktop/BGD_Repos/combat_biovar/data/ukb_to_model/UKB_CN_data_simsites.csv")

#years for plotting
raw_df <- raw_df %>%
  mutate(age_years = age_days/365.25)

@@

pulled variance from cubic using `scp -r 'gardnerm@cubic-login.uphs.upenn.edu:/cbica/home/gardnerm/combat-biovar/ukb_basic/centile_csvs/*_variance.csv' ./derivatives/ukb_basic`

Get predicted centiles
- pulled from cubic using `scp -r 'gardnerm@cubic-login.uphs.upenn.edu:/cbica/home/gardnerm/combat-biovar/ukb_basic/centile_csvs/*_predictions.csv' ./derivatives/ukb_basic`

@@

  # Add a "Source_File" column with the file name
  data <- data %>%
    mutate(Source_File = as.factor(basename(file))) %>%
    mutate(dataset = gsub("_data|_predictions.csv", "", Source_File))

@@

unique(combined_preds$dataset)

skim(combined_preds)
```

@@

Get errors
- pulled centile/z error calcs from cubic using `scp -r 'gardnerm@cubic-login.uphs.upenn.edu:/cbica/home/gardnerm/combat-biovar/ukb_basic/centile_csvs/*_diffs.csv' ./derivatives/ukb_basic`

@@

sum(is.na(diffs.df))
```

Get subject-wise summaries
- pulled from cubic using `scp -r 'gardnerm@cubic-login.uphs.upenn.edu:/cbica/home/gardnerm/combat-biovar/ukb_basic/centile_csvs/subject-wise/*.csv' ./derivatives/ukb_basic`

@@

sum(is.na(subj_sum.df))
```

@@

```{r, }
full_cent_res <- centile.t.tests.full_result(diffs.df, feature_list=pheno_abs.diff.list)
saveRDS(full_cent_res, "./derivatives/ukb_basic/featurewise_cent_t_tests_all_out.RDS") #running once and saving because it takes a long time
```

@@

Little plot
```{r}
#get means w/in feature 
mean.diffs.long <- diffs.df %>%
  dplyr::select(sex, dataset, pheno_abs.diff.list) %>%
  dplyr::filter(!grepl('_refA', dataset)) %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("raw", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE)) %>%
  group_by(dataset) %>%
  summarize(across(starts_with("abs.diff_"), mean)) %>%
  ungroup() %>%
  pivot_longer(cols=starts_with("abs.diff_"), values_to="centile_abs.diff", names_to = "pheno", names_prefix = "abs.diff_") %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)),
      label = sub("_[^_]*_", "_", pheno))
```

```{r}
dataset_names <- c(raw = "Raw Data", cf = "ComBat w/o Covar", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")
dataset_colors <- c(cf = "#3D5983FF", cf.lm = "#5A8A54FF", cf.gam ="#262626FF", cf.gamlss ="#CFB023FF")

cent.diffs.plot <- mean.diffs.long %>%
  dplyr::filter(dataset != "raw") %>%
  mutate(centile_abs.diff = centile_abs.diff*100) %>% #for visuals
  ggplot() +
  geom_histogram(aes(x=centile_abs.diff, fill=dataset, y = stat(width*density)), color="black", alpha=0.6, position="identity") +
  theme_linedraw(base_size = 11) +
  facet_wrap(~pheno_cat) +
  scale_y_continuous(labels = scales::percent) + 
  scale_fill_manual(values=dataset_colors, name = "ComBat \nConfiguration", labels=dataset_names) +
  labs(y="Percent Features", x = "Mean Absolute Centile Error") +
  ggtitle("Absolute errors in centile scores of brain structure features across ComBat processing pipelines")
cent.diffs.plot

@@

```{r}
dataset_names <- c(raw = "Raw Data", cf = "ComBat w/o Covar", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")

@@

global_cent_errs_plot <- global_abs.diffs %>%
  dplyr::filter(dataset == "cf.lm" | dataset == "cf.gam" | dataset == "cf.gamlss") %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("raw", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         pheno = factor(pheno, levels = c("WMV", "GMV", "sGMV", "Ventricles"), ordered = TRUE),
         abs.diff = abs.diff*100) %>% #for visuals
  ggplot(aes(pheno, abs.diff)) +
  geom_violin(aes(x=pheno, y=abs.diff, fill=dataset, color=dataset), scale="count") +
  theme_linedraw(base_size = 11) +
  scale_fill_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  #WMV
geom_signif(y_position = c(3, 3.5, 2.5), xmin = c(0.7, 0.7, 1),
              xmax = c(1, 1.3, 1.3), annotation = c("***","***", "***"),
              tip_length = 0, vjust = 0.6) +
  #GMV
  geom_signif(y_position = c(2.75, 3.25, 2.25), xmin = c(1.7, 1.7, 2),
              xmax = c(2, 2.3, 2.3), annotation = c("***","***", "***"),
              tip_length = 0, vjust = 0.6) +
  #sGMV
  geom_signif(y_position = c(2.7, 3.2, 2.2), xmin = c(2.7, 2.7, 3),
              xmax = c(3, 3.3, 3.3), annotation = c("***","***", "***"),
              tip_length = 0, vjust = 0.6) +
  #Ventricles
  geom_signif(y_position = c(7.1, 6.75, 6.45), xmin = c(3.7, 3.7, 4),
              xmax = c(4, 4.3, 4.3), annotation = c("***","***", "***"),
              tip_length = 0, vjust = 0.6) +
  labs(y="Absolulte Centile Error", x = "Feature") +
  theme(plot.title = element_text(size=12))
global_cent_errs_plot
# ggsave("figs/global_centile_errors.jpeg", global_cent_errs_plot)
```

All features:
```{r}
long_abs.diffs <- diffs.df %>%
  dplyr::filter(dataset == "cf.lm" | dataset == "cf.gam" | dataset == "cf.gamlss") %>% #drop refA levels
  dplyr::select(participant, sex, age_days, sim.site, dataset, paste0("abs.diff_", pheno_list)) %>%
  pivot_longer(cols=starts_with("abs.diff_"), names_to="pheno", names_prefix="abs.diff_", values_to = "abs.diff") %>%
  mutate(dataset = factor(dataset, levels = c("raw", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         abs.diff = abs.diff*100,
         pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)))

long_abs_diff.plt <- long_abs.diffs %>%
  ggplot(aes(pheno, abs.diff)) +
  geom_violin(aes(x=pheno, y=abs.diff, fill=dataset, color=dataset), scale="count") +
  theme_linedraw(base_size = 11) +
  scale_fill_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  labs(y="Absolulte Centile Error", x = "Feature") +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust=0.4, size=6), legend.position="top") +
  facet_wrap(~pheno_cat, nrow=4, scales="free")
ggsave("figs/all_abs_err_plt_wlabels.jpeg", long_abs_diff.plt, width=13, height=10.5, units="in")
```

plot median on brain
```{r}
#get median w/in feature 
med.diffs.long <- diffs.df %>%
  dplyr::select(sex, dataset, pheno_abs.diff.list) %>%
  dplyr::filter(dataset %in% c("cf.lm", "cf.gam", "cf.gamlss")) %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("raw", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE)) %>%
  group_by(dataset) %>%
  summarize(across(starts_with("abs.diff_"), median)) %>%
  ungroup() %>%
  pivot_longer(cols=starts_with("abs.diff_"), values_to="median_centile_abs.diff", names_to = "pheno", names_prefix = "abs.diff_") %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)),
      label = sub("_[^_]*_", "_", pheno))

@@

dataset_names <- c(raw = "Raw Data", cf = "ComBat w/o Covar", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")
#var plot
med.diffs.plot.df <- med.diffs.long2 %>%
  dplyr::filter(pheno_cat != "Global Volume") %>%
  dplyr::filter(!grepl('_refA', dataset)) %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("raw", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         median_centile_abs.diff = median_centile_abs.diff*100)

med.diffs.plot <- ggplot(med.diffs.plot.df) +
  theme_linedraw(base_size=12) +
  ggseg::geom_brain(atlas = dk_nomed, 
             position = position_brain(hemi ~ side),
             aes(fill = median_centile_abs.diff)) +
  facet_grid(dataset ~ pheno_cat, labeller = labeller(dataset = as_labeller(dataset_names))) + 
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=2/3, plot.margin = margin(1,1,1,1, 'pt')) +
  paletteer::scale_fill_paletteer_c("grDevices::Oslo", name = "Median Absolute Centile Error", limits = c(0, 1)) #
# med.diffs.plot
```

```{r}
#plot global
med.diffs.plot.global.df <- med.diffs.long2 %>%
  dplyr::filter(pheno_cat == "Global Volume") %>%
  dplyr::filter(!grepl('_refA', dataset)) %>% #drop refA levels
  dplyr::select(!c(label, region, hemi)) %>% #drop cols corresponding to dk regions
  mutate(dataset = factor(dataset, levels = c("raw", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         median_centile_abs.diff = median_centile_abs.diff*100)

med.diffs.plot.global <- ggplot(med.diffs.plot.global.df) +
  ggseg::geom_brain(atlas = aseg_cerebrum, 
             aes(fill = median_centile_abs.diff),
             side = c("coronal")) +
  #scale_fill_gradient2() +
  facet_grid(dataset~pheno_cat) + 
  theme_linedraw(base_size=12) +
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=, plot.margin = margin(1,1,1,1, 'pt'), strip.text.y = element_blank()) +
  paletteer::scale_fill_paletteer_c("grDevices::Oslo", name = "Median Absolute Centile Error", limits = c(0, 1))
# med.diffs.plot.global
```

Combine plots - need to keep playing around to make the spacing pretty when it saves out
```{r}
p_diff <- ggarrange(
  med.diffs.plot.global, med.diffs.plot,
  ncol=2, nrow=1, 
  widths = c(.95, 3.1),
  #labels=c("A", "B"),
  #hjust=0.01,
  align = "hv",
  common.legend = TRUE, legend = "bottom"
  )
```

Count of instances where cf.gamlss has higher errors

```{r}
full_cent_res %>%
  dplyr::filter(sig_fdr == TRUE & bigger_group == "cf.gamlss") %>%
  group_by(comp) %>%
  summarise(n_regions=sum(sig_fdr))
```

13 regions where ComBat GAM is better than ComBat-LS, 13 regions where linear ComBat is better than ComBat-LS, 1 region where combat w/o covars is better: ALL cortical thickness

@@

check for skew (welch t.test vs ranked welch t test)
```{r}
for (pheno in pheno_list){
  val <- paste0("diff_", pheno)
  p <- ggplot(diffs.df, aes(x = diffs.df[[val]], fill= sex, color=sex)) +
      geom_histogram(alpha=0.5, position="identity") +
    ggtitle(val) +
    facet_wrap(~dataset, scales="free")
print(p)
}
```

```{r}
for (cf in c("cf.gam", "cf.gamlss")) {
  for (pheno in vol_list_global){
  val <- paste0("diff_", pheno)
  med.df <- diffs.df %>%
    dplyr::filter(dataset == cf) %>%
    group_by(sex) %>%
    summarize_at(val, median, na.rm=FALSE)

@@

```{r, message=FALSE, }
sex_t_tests_in_feat.df <- sex.bias.feat.t.tests(diffs.df, feature_list=pheno_diff_list)
saveRDS(sex_t_tests_in_feat.df, "./derivatives/ukb_basic/featurewise_cent_sexbias_all_out.RDS")
```

@@

@@

```{r}
dataset_names <- c(raw = "Raw Data", cf = "ComBat w/o Covar", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")
#var plot
sex.var.plot.df <- sex_t_tests_to_plot %>%
  dplyr::filter(pheno_cat != "Global Volume") %>%
  dplyr::filter(dataset %in% c("cf.lm", "cf.gam", "cf.gamlss")) %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("raw", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         median_sex_diff = median_sex_diff*100)
#find range
max(sex.var.plot.df$median_sex_diff, na.rm=TRUE)
min(sex.var.plot.df$median_sex_diff, na.rm=TRUE)
